|

### 2020-05-18 paper/Manuscript.Rmd
Integrate Aaron's edits

A different class of solutions instead focuses on the practical issue of *how* researchers can meet the requirements of open science. <!--limitation of signalling approaches, that WORCS addresses, is that they do not clarify One could use WORCS to meet the TOP-guidelines, and document this in a TOP-statement.--> One notable example here is the workflow for reproducible analyses developed by @peikertReproducibleDataAnalysis2019. Being limited to computational reproducibility, this workflow only addresses TOP-guidelines 2, 3, and 5. Peikert and Brandmaier's workflow builds upon the same general principles making it fully compatible with the solution proposed here. Their workflow aims to encompass even the most sophisticated analytic strategies and is hence relatively complex itself. WORCS greatly simplifies matters by assuming that no other software then R Packages are needed <!-- difference docker -->and that that a single data file is sufficient <!-- difference make -->. If both assumptions are met, and they routinely are, this eschews much overhead of Peikert and Brandmaier's workflow resulting in a much more lightweight approach to safeguard computational reproducibility under *most circumstances*. WORCS addresses a unique issue not covered by existing solutions, namely to provide a workflow most conducive to satisfying the TOP-guidelines, while being compatible with existing approaches.

@@

<!-- LB: and onwards: this section requires some background knowledge on R/packages/etc. This could be a place where readers stumble and stop reading. Perhaps introduce the concept of the R project template earlier, to see section on dependencies more into perspective. 
[main issue] it should become clear earlier what the WORCS workflow entails: e.g. switching to working with a particular R Project Template. Discuss the ‘workflow' section earlier. Related: Can you make a schematic overview of the WORCS?overview--> 
Many solutions exist to ensure computational reproducibility. These solutions typically work by enveloping your research project in a distinct "environment" that only has access to programs that are explicitly installed, and maintaining a record of these programs. These solutions differ in user-friendliness and effectiveness. If strict reproducibility is required, one might use the aforementioned Docker-based workflow by @peikertReproducibleDataAnalysis2019, which runs all analyses inside a virtual machine, that can be stored like a sort of time capsule and identically reinstated on different systems. This is effective, and also pertains to software outside the R environment (e.g., preprocessing tools for neuroimaging data). <!--For small projects, or novice users || Mention CodeOcean here-->A slightly less sophisticated solution is offered by the R-package `packrat`, which installs all software used in a project to a dedicated library that can be stored and copied with the project. This solution is reasonably user-friendly and effective, but has the disadvantage that for each project, all packages must be installed anew, which can take a long time (sometimes hours) and a lot of hard drive space. Moreover, Git/GitHub is not designed to store your entire project library, so `packrat` does not address the issue of how other users are supposed to get access to your library. In conclusion, `packrat` is somewhat unwieldy. The package `checkpoint` offers an extremely lightweight solution: Instead of storing all software used, it simply records the calendar date, and then installs the version of all required packages that was available on the central R repository `CRAN` on that date from an archival website. Thus, all that is needed to restore a project is the date on which it was conducted. This is very user-friendly, and reasonably effective - the only problem is that this solution is limited to `CRAN` packages, and cannot mix package versions from different dates.

@@

@@

## Outlook

<!-- not sure where this repro integration section belongs -->
The `worcs`-package integrates several reproducibility tools into a convenient workflow by assuming reasonable standards that fulfil most researches needs. Currently, however, if a researcher prefers to use other tools that are conceptually similar, they have to leave WORCS behind. We currently integrate WORCS into a modular framework of reproducibility tools for R [@repro], which will serve as the backend for WORCS. This ongoing integration into a unifying framework does not compromise the ease of use for the researcher. However, it gives them more flexibility to satisfy the demands of their research projects while meeting the TOP-guidelines.

>>>>

A different class of solutions instead focuses on the practical issue of *how* researchers can meet the requirements of open science. <!--limitation of signalling approaches, that WORCS addresses, is that they do not clarify One could use WORCS to meet the TOP-guidelines, and document this in a TOP-statement.--> One notable example is the workflow for reproducible analyses developed by @peikertReproducibleDataAnalysis2019. Because that workflow focuses on computational reproducibility, it only addresses TOP-guidelines 2, 3, and 5. Moreover, in striving to ensure strict computational reproducibility for even the most sophisticated analyses, Peikert and Brandmaier's workflow ends up being relatively complex to implement. WORCS is designed to be a simple and sufficient solution for projects that can be conducted entirely within R. It eschews much overhead of Peikert and Brandmaier's workflow, resulting in a much more lightweight approach to safeguard computational reproducibility under *most circumstances*. Importantly, WORCS builds upon the same general principles as Peikert and Brandmaier, which means the two workflows are compatible. Finally, WORCS addresses a unique issue not covered by other existing solutions, namely to provide a workflow most conducive to satisfying the TOP-guidelines, while being compatible with existing approaches.

@@

<!-- LB: and onwards: this section requires some background knowledge on R/packages/etc. This could be a place where readers stumble and stop reading. Perhaps introduce the concept of the R project template earlier, to see section on dependencies more into perspective. 
[main issue] it should become clear earlier what the WORCS workflow entails: e.g. switching to working with a particular R Project Template. Discuss the ‘workflow' section earlier. Related: Can you make a schematic overview of the WORCS?overview--> 
Many solutions exist to ensure computational reproducibility. These solutions typically work by enveloping your research project in a distinct "environment" that only has access to programs that are explicitly installed, and maintaining a record of these programs. These solutions differ in user-friendliness and effectiveness. If strict reproducibility is required, one might use the aforementioned Docker-based workflow by @peikertReproducibleDataAnalysis2019, which runs all analyses inside a virtual machine that can be stored like a sort of time capsule, and identically reinstated on different systems. This is effective, and also pertains to software outside the R environment (e.g., preprocessing tools for neuroimaging data). <!--For small projects, or novice users || Mention CodeOcean here-->A slightly less sophisticated solution is offered by the R-package `packrat`, which installs all software used in a project to a dedicated library that can be stored and copied with the project. This solution is reasonably user-friendly and effective, but has the disadvantage that for each project, all packages must be installed anew, which can take a long time (sometimes hours) and a lot of hard drive space. Moreover, Git/GitHub is not designed to store your entire project library, so `packrat` does not address the issue of how other users are supposed to get access to your library. In conclusion, `packrat` is somewhat unwieldy. The package `checkpoint` offers an extremely lightweight solution: Instead of storing all software used, it simply records the calendar date, and then installs the version of all required packages that was available on the central R repository `CRAN` on that date from an archival website. Thus, all that is needed to restore a project is the date on which it was conducted. This is very user-friendly, and reasonably effective - the only problem is that this solution is limited to `CRAN` packages, and cannot mix package versions from different dates.

@@

## Future developments

The WORCS procedure and accompanying R-package provide a user-friendly and lightweight workflow for open, reproducible research in R, that meets all TOP-guidelines. It is beyond the scope of WORCS to support the incorporation of tools outside of the R-environment, or to containerize a project so that it can be identically reinstated on a different system or virtual machine. One important area of future development is to enable these extensions of the workflow. To this end, we are integrating WORCS into a modular framework of reproducibility tools for R [@repro]. This will make it possible for researchers to enhance a WORCS project with strict reproducibility tools like 'Docker' and 'Make', or vice versa, to initiate a WORCS project in a strictly reproducible environment. This combines the strengths of WORCS with those of @peikertReproducibleDataAnalysis2019.

@@
